### 2013-07-07 inst/doc/vingette.Rmd
updated README based on inst/doc/vignette.Rmd

```{r}
install.packages("uuid",,'http://rforge.net/',type='source')
library("devtools")
install_github("XMLSchema", "omegahat")
install_github("reml", "ropensci")
library("reml")
```

@@

```{r publish_figshare, eval=FALSE} <!-- We don't want to generate a DOI every time we run the vignette -->
id = eml_publish("my_eml_data.xml", description="Example EML file from reml", categories = "Ecology", tags = "EML")
```

In return, figshare provides the object with a DOI, which is added to the EML.

>>>>

```{r, results="hide", message=FALSE, warning=FALSE, eval=FALSE}
install.packages("uuid",,'http://rforge.net/',type='source')
library("devtools")
install_github("XMLSchema", "omegahat")
install_github("reml", "ropensci")
```

Load the package:

```{r, results="hide", message=FALSE, warning=FALSE}
library("reml")
```

@@

```{r publish_figshare, eval=FALSE} <!-- We don't want to generate a DOI every time we run the vignette -->
id = eml_publish("my_eml_data.xml", description="Example EML file from reml", categories = "Ecology", tags = "EML", destination="figshare")
```

`eml_publish` 
In return, figshare provides the object with a DOI, which is added to the EML.
